% ==============================================================================
%
%                             Glossary
%
% ==============================================================================
\newglossaryentry{vivadohlx}
{
    name=Vivado HLx,
    description={Xilinx tool used for synthesis, implementation and debugging}
}
\newglossaryentry{vivadohls}
{
    name=Vivado HLS,
    description={Xilinx tool used for high level synthesis. Hardware is
    described in C/C++ language that is synthesized by the tool to hardware
    description language.}
}
\newglossaryentry{ila}
{
    name=integrated logic analyzer (ILA),
    description={Can be configured to record FPGA internal signals and send to PC}
}
\newglossaryentry{diip}
{
    name=Distributed Image Processing (diip),
    description={Project nickname of the bachelor thesis}
}
\newglossaryentry{rmse}
{
    name=root mean square error (RMSE),
    description={Used as a metric to measure the difference in two images}
}
\newglossaryentry{bramtile}
{
    name=BRAM tile,
    description={A single block ram instance on the FPGA. In this case one tile
    can be configured as either one 36Kb RAM or two inpdependant 18Kb RAM}
}
\newglossaryentry{ghdl}
{
    name=ghdl,
    description={Open-source simulator used for simulating VHDL entities}
}
\newglossaryentry{ipcore}
{
    name=IP core,
    description={Intellectual Property core. Functional blocks that are
    connected together and form the FPGA configuration. IP cores can be bought
    or developed.}
}
\newglossaryentry{rtl}
{
    name=RTL,
    description={Register transfer level. Design abstraction which models a
    synchronous digital circuit in terms of dataflow between hardware
    registers.}
}
\newglossaryentry{fifo}
{
    name=FiFo,
    description={First-in First-out databuffer. Data written is read in the
    same order. Data can only be read once.}
}
\newglossaryentry{uft}
{
    name=UDP File Transfer (UFT),
    description={The session protocol introduced in the preceeding project
    implemented on
    the FPGA used to transfer image data to and from the FPGA.}
}
\newglossaryentry{opencv}
{
    name=OpenCV,
    description={Open-source image processing library used in the C/C++ PC
    software.}
}
\newglossaryentry{duv}
{
    name=device under validation (DUV),
    description={An entity that is tested inside a testbench.}
}